Dissertation Manuscript

### 2023-10-30 paper.qmd
improve format selection

  <!--  <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/manuscript.pdf.md" target="manuscript"> -->
  <!-- <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscript-md -->
  <!-- </a>  -->

</p>

>>>>

  <!--  <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/manuscript.pdf.md" target="manuscript"> -->
  <!-- <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscript-md -->
  <!-- </a>  -->
  <br>
  <span>Click buttons above to select format or download</span>
</p>
